Evaluation

### 2018-03-31 FlairResearch/Paper.tex
Changed the BoxPlot graphs and Average lines graphs, fixed the Benchmark table, and added stuff to paper about individual graphs.

		To assess the rate of failure we used the methods described in \ref{methods} to find the percentage of applications in each test which failed. The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{28.54 percent} of applications on average across all runs. This was primarily because DIALDroid would attempt to allocate more than our allotted 14 GB of memory, which was more than twice that allocated to any of the other tools. SEALANT, Covert, Didfail, and Flair all were able to run without any memory issues with far less memory. Therefore, Flair is able to analyze applications as reliably in terms of failure rate as well as SEALANT, Covert, and Didfail, while analyzing applications more reliably than DIALDroid.

@@

\scriptsize
\centering
	\vspace{+0.3cm}
	%\caption{Comparison between \@name, DidFail, and AmanDroid. TP, FP and FN are represented by symbols \tp, \fp, \fn, respectively. (X\#) indicates the number \# of detected instances for the corresponding symbol X.  
	%\label{table_comparison}}
	\begin{tabular}{|p{0.07cm}|l|l|l|l|l|p{0.8cm}|}
		\hline
		& Test Case & DidFail & SEALANT &  DIALDroid & Covert & Flair \\ %DroidGuard \\
		\hline
		\hline
		%\multicolumn{7}{|c|}{\cellcolor{light-gray}DroidBench2}\\\hline
		\parbox[t]{2mm}{\multirow{23}{*}{\rotatebox[origin=c]{90}{DroidBench2}}}
		%\parbox[t]{2mm}{\multirow{16}{*}{\rotatebox[origin=c]{90}{IPC}}}
		&ICC\_bindService1    &\fp \fn &\tp &\tp	 &\tp	&\tp		\\
		&ICC\_bindService2    &\fn &\tp	&\fn &\tp &\tp			\\
		&ICC\_bindService3    &\fn &\tp	&\fn &\tp &\tp			\\
		&ICC\_bindService4    &\fp \scriptsize (\fn \scriptsize 2)	&(\tp \scriptsize 2) &\tp\fn &\scriptsize (\tp \scriptsize 2) &\scriptsize (\tp \scriptsize 2)	\\
		&ICC\_sendBroadcast1  &\tp &\tp &\tp &\tp &\tp \\
		&ICC\_startActivity1  &\fn &\fn &\tp &\tp &\tp \\
		&ICC\_startActivity2  &\fn	&\tp	&\tp	&\tp &\tp \\
		&ICC\_startActivity3  &\fn	&\tp	&\tp	&\tp &\tp \\
		&ICC\_startActivity4  &\fp	&	&\fn &	& 	\\
		&ICC\_startActivity5  &\scriptsize (\fp \scriptsize 2)	&\fn	&\fn\ & &	\\
		&ICC\_startActivityForResult1 	&\fn	&\tp &\tp &\tp	&\tp\\
		&ICC\_startActivityForResult2 &\fn &\tp &\tp &\tp &\tp\\
		&ICC\_startActivityForResult3 &\fn &\t- &\fn	&\tp	&\tp\\
		&ICC\_startActivityForResult4 &\scriptsize (\fn \scriptsize 2)	&\tp\fn	&\tp\fn  & \scriptsize (\tp \scriptsize 2)	& \scriptsize (\tp \scriptsize 2)\\
		&ICC\_startService1   &\fp \tp &\fn &\tp	&\tp &\tp\\
		&ICC\_startService2   &\fp \tp &\fn &\tp &\tp &\tp\\
		%\cline{2-7}
		%\parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{C.Provider}}}	
		&ICC\_delete1		&\fn	&\fn &\fn 	&\tp	&\tp	\\
		&ICC\_insert1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
		&ICC\_query1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
		&ICC\_update1		&\fn	&\fn  &\fn	&\tp	&\tp	\\
		%\cline{2-7}
		%\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{IAC}}}	
		&IAC\_startActivity1	 &\tp \fp &\fn &\fn	&\tp	&\tp\\
		&IAC\_startService1  &\tp &\fn &\fn &\tp &\tp\\
		&IAC\_sendBroadcast1 &\tp &\fn &\fn &\tp	&\tp\\
		\hline
		\parbox[t]{2mm}{\multirow{9}{*}{\rotatebox[origin=c]{90}{ICC-Bench}}}
		%\multicolumn{7}{|c|}{ICC-Bench}\\\hline
		&Explicit\_Src\_Sink &\fn &\fn &\tp &\tp &\tp\\		
		&Implicit\_Action  &\tp &\fn &\tp & \tp &\tp\\
		&Implicit\_Category  &\tp &\fn &\tp &\tp &\tp\\
		&Implicit\_Data1 &\tp &\fn &\tp &\tp  &\tp\\
		&Implicit\_Data2 &\tp &\fn &\tp &\tp  &\tp\\
		&Implicit\_Mix1 &\tp &\tp &\tp &\tp  &\tp\\
		&Implicit\_Mix2 &\tp &\fn &\tp &\tp  &\tp\\
		&DynRegisteredReceiver1 &\fn &\fn &\tp &\fn &\fn\\ 	
		&DynRegisteredReceiver2 &\fn &\fn &\tp &\fn &\fn\\ 			
		\hline		
		\multicolumn{2}{|l|}{\textbf{Precision}}& 55\%&XX\%&XX\%&100\%&100\%\\
		\hline
		\multicolumn{2}{|l|}{\textbf{Recall}}& 37\%&XX\%&XX\%&97\%&97\%\\
		\hline
		\multicolumn{2}{|l|}{\textbf{F-measure}}& 44\%&XX\%&XX\%&98\%&98\%\\
		\hline
		\hline
\end{tabular}
\end{table*}

>>>>

		To assess the rate of failure we used the methods described in \ref{methods} to find the percentage of applications in each test which failed. The data we collected shows that while Covert, SEALANT, Didfail, and Flair do not fail to analyze any of the applications, DIALDroid failed a significant \textit{28.54 percent} of applications on average across all runs. This was primarily because DIALDroid would attempt to allocate more than our allotted 14 GB of memory, which was more than twice that allocated to any of the other tools. SEALANT, Covert, Didfail, and Flair all were able to run without any memory issues with far less memory. Therefore, Flair is able to analyze applications as reliably in terms of failure rate as well as SEALANT, Covert, and Didfail, while analyzing applications more reliably than DIALDroid.\\
		\paragraph{In case we use five different graphs:}
		\subparagraph{Didfail Graph:} 
		The box plots in \c.p{Didfail box plot graph} show the spread and symmetry of the time it took Didfail to analyze the seven different bundles of applications. Didfail's analysis tends to skew to the right, and overall is not very symmetrical. Also, Didfail has an increasing IQR spread as the size of the bundles increases.
		\subparagraph{SEALANT Graph:}
		\c.p{SEALANT box plot graph} shows the spread of analysis times for SEALANT across the seven bundles. SEALANT maintains a relatively consistent spread and IQR of analysis times as the sizes of bundles increases. SEALANT also have very symmetrical data.
		\subparagraph{DIALDroid Graph:}
		The box plot graph for DIALDroid is presented in \c.p{DIALDroid box plot graph}. This data shows that DIALDroid, like Didfail tends to have data that skews right, but DIALDroid's analysis times become slightly more symmetrical as the size of the bundles increase. The IQR, though, grows slightly as the bundle size increases, showing greater variability in analysis times.
		\subparagraph{Covert Graph:}
		\c.p{Covert Box plot graph} shows the box plot data for Covert's analysis times. This data shows that Covert's analysis times across our seven bundles was extremely skewed right when the bundles size was small, but then became increasingly symmetrical as the size of the bundle increased. The IQR and spread, though, started out small and grew considerably as the bundle size increased. It is apparent that as the bundles sizes increase Covert's analysis times become far more variable.
		\subparagraph{Flair Graph:}
		The data in \c.p{Flair box plot graph} shows the spread and symmetry information for Flair's analysis times. This data shows that Flair is able to maintain extremely low analysis times for increasing bundle sizes. This is due to its iterative process. Flair only has to analysis applications that are added to the bundle, not the whole bundle. This allows Flair to maintain analysis times far below the other tool. Flair also maintains lower IQR ranges, showing that Flair is more consistent overall.

@@

\scriptsize
\centering
	\vspace{+0.3cm}
	%\caption{Comparison between \@name, DidFail, and AmanDroid. TP, FP and FN are represented by symbols \tp, \fp, \fn, respectively. (X\#) indicates the number \# of detected instances for the corresponding symbol X.  
	%\label{table_comparison}}
	\begin{tabular}{|p{0.07cm}|l|l|l|l|l|p{1.3cm}|}
		\hline
		& Test Case & Covert & DIALDroid &  Didfail & Flair & SEALANT \\ %DroidGuard \\
		\hline
		\hline
		%\multicolumn{7}{|c|}{\cellcolor{light-gray}DroidBench2}\\\hline
		\parbox[t]{2mm}{\multirow{23}{*}{\rotatebox[origin=c]{90}{DroidBench2}}}
		%\parbox[t]{2mm}{\multirow{16}{*}{\rotatebox[origin=c]{90}{IPC}}}
		&ICC\_bindService1    &\tp &\tp &\fp \fn	 &\tp	&\tp		\\
		&ICC\_bindService2    &\tp &\fn	&\fn &\tp &\tp			\\
		&ICC\_bindService3    &\tp &\fn	&\fn &\tp &\tp			\\
		&ICC\_bindService4    &\scriptsize (\tp \scriptsize 2)	&\tp \fn &\fp \scriptsize (\fn \scriptsize 2) &\scriptsize (\tp \scriptsize 2)	 &\scriptsize (\tp \scriptsize 2)	\\
		&ICC\_sendBroadcast1  &\tp &\tp &\tp &\tp &\tp \\
		&ICC\_startActivity1  &\tp &\tp &\fn &\tp &\fn \\
		&ICC\_startActivity2  &\tp	&\tp	&\fn	&\tp &\tp \\
		&ICC\_startActivity3  &\tp	&\tp	&\fn	&\tp &\tp \\
		&ICC\_startActivity4  & 	&	&\fp &	& 	\\
		&ICC\_startActivity5  &	&	&\scriptsize (\fp \scriptsize 2) & &	\\
		&ICC\_startActivityForResult1 	&\tp	&\tp &\fn &\tp	&\tp\\
		&ICC\_startActivityForResult2 &\tp &\tp &\fn &\tp &\tp\\
		&ICC\_startActivityForResult3 &\tp &\fn &\fn	&\tp	&\tp\\
		&ICC\_startActivityForResult4 &\scriptsize (\tp \scriptsize 2)	&\tp\fn	&\scriptsize (\fn \scriptsize 2)  &\scriptsize (\tp \scriptsize 2) &\tp\fn \\
		&ICC\_startService1   &\tp &\tp &\fp\tp	&\tp &\fn\\
		&ICC\_startService2   &\tp &\tp &\fp\tp &\tp &\fn\\
		%\cline{2-7}
		%\parbox[t]{2mm}{\multirow{4}{*}{\rotatebox[origin=c]{90}{C.Provider}}}	
		&ICC\_delete1		&\tp	&\fn &\fn 	&\tp	&\fn	\\
		&ICC\_insert1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
		&ICC\_query1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
		&ICC\_update1		&\tp	&\fn  &\fn	&\tp	&\fn	\\
		%\cline{2-7}
		%\parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{IAC}}}	
		&IAC\_startActivity1	 &\tp &\fn &\fp\tp	&\tp	&\fn\\
		&IAC\_startService1  &\tp &\fn &\tp &\tp &\fn\\
		&IAC\_sendBroadcast1 &\tp &\fn &\tp &\tp	&\fn\\
		\hline
		\parbox[t]{2mm}{\multirow{9}{*}{\rotatebox[origin=c]{90}{ICC-Bench}}}
		%\multicolumn{7}{|c|}{ICC-Bench}\\\hline
		&Explicit\_Src\_Sink &\tp &\tp &\fn &\tp &\fn\\		
		&Implicit\_Action  &\tp &\tp &\tp & \tp &\fn\\
		&Implicit\_Category  &\tp &\tp &\tp &\tp &\fn\\
		&Implicit\_Data1 &\tp &\tp &\tp &\tp  &\fn\\
		&Implicit\_Data2 &\tp &\tp &\tp &\tp  &\fn\\
		&Implicit\_Mix1 &\tp &\tp &\tp &\tp  &\tp\\
		&Implicit\_Mix2 &\tp &\tp &\tp &\tp  &\fn\\
		&DynRegisteredReceiver1 &\fn &\tp &\fn &\fn &\fn\\ 	
		&DynRegisteredReceiver2 &\fn &\tp &\fn &\fn &\fn\\ 			
		\hline		
		\multicolumn{2}{|l|}{\textbf{Precision}}& 100\%&XX\%&55\%&100\%&XX\%\\
		\hline
		\multicolumn{2}{|l|}{\textbf{Recall}}& 97\%&XX\%&37\%&97\%&XX\%\\
		\hline
		\multicolumn{2}{|l|}{\textbf{F-measure}}& 98\%&XX\%&44\%&98\%&XX\%\\
		\hline
		\hline
\end{tabular}
\end{table*}
